Lattices of acyclic pipe dreams

### 2023-03-17 acyclicFacets/draft/latticePipeDreams.tex
added Remark 5.29 about connection between our sweeping algorithm and the algorithm of Jahn-Stump

Although the algorithm presented in~\cite{JahnStump} is more general, our sweeping algorithm is more direct when computing the output for the input $\pi$, since we skip the step of translating the conditions on the sign of $f(\rootFunction{I^j}{j})$ in Jahn-Stump's algorithm. We remark that these two algorithms were developed independently, while approaching different problems. This highlights the relevance of the sweeping algorithm.  
\end{remark}

>>>>

Although the algorithm presented in~\cite{JahnStump} is more general, we highlight that our sweeping algorithm is conceptually simpler, since we skip the step of translating the conditions on the sign of $f(\rootFunction{I^j}{j})$ in Jahn-Stump's algorithm. We remark that these two algorithms were developed independently, while approaching different problems. This shows that the sweeping algorithm has a significant importance in the combinatorial and geometric understanding of subword complexes.  
\end{remark}
